\section{Checkpoint 4}

% align with slide numbers
\addtocounter{subsection}{1}

\subsection{What is the role of the Memory Management Unit (MMU)}
Sie übersetzt logische (Adresse im Programm) auf physikalische Adressen (Adresse auf Festplatte).
(Passiert bei jedem Speicherzugriff neu.)

\subsection{What is the difference between virtual / logical Adresses and physikal adresses?}

\subsection{What is Segmentation?}

\subsection{What are the main shortcommings of Segmentation?}

\subsection{Describe Paging. How is it different from Segmentation, and how does it address the shortcumings of Segmentation?}

\subsection{Describe the layout of a Page Table. Why do some architectures use multi-level page table structures?}

\subsection{Name two bits associated with each Page Table Entry and describe their purpose.}

\subsection{What is the role of the Translation Lookaside Buffer (TLB)?}

\subsection{Assume a memory system that manages adresses of 26 bits length, with a page size of 256 bytes. How many entries does a page table have?}

\subsection{What is the size of the virtual adress space?}

\subsection{How long are the adresses page number and offset?}

\subsection{Each page table entry has two status bits.}

\subsection{What is the length of a page table entry?}

\subsubsection{What is the total size of a page table?}

\subsection{Assume the described system has access to 24MiB of physical memory, half of which is reserved for the operating system. Of this half, 5MiB are reserved for process page tables, and are not pageable. How many processes can this system support?}

\subsection{What is the maximum size of a process working set, assuming that no reserved OS pages are part of the working set?}

\subsection{What is a Page Fault?}

\subsection{What is the difference between a Soft Page Fault and a Hard Page Fault?}

\subsection{Name two different reasons for which a memory access coul produce a Page Fault.}

\subsection{What is a Working Set?}

\subsection{What is the role of the Modified, Standby, Free, Zero and Bad Page Lists? What properties do pages in these lists have? How do pages transition between these lists?}

\subsection{What is the purpose of the Page Frame Number Database?}

\subsection{Describe the page replacement algorithms First-In-First-Out (FIFO), Second Chance, and Least-Recently-Used (LRU).}

\subsection{What is Béládys Anomaly, as found in the FIFO page replacement algoritm?}

\subsection{Assuming three frames of physical memory, and a memory access pattern to the virtual pages: 2,1,4,2,3,4,2,1,3,4,3. How many Page Fault would FIFO incur?}

\subsection{How many Page Faults would Second Chance incur?}

\subsection{How many Page Faults would LRU incur?}

\subsection{What is the difference between swapping and page replacement (paging)?}

\subsection{Describe the difference between reserved and committed memory.}

\subsection{What is a Guard Page? What could it be used for?}

\subsection{How do operating systems implement shared memory?}

\subsection{What is Copy-on-Write (CoW) memory, and what is it used for?}
